Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-19 paper.tex
sec4 intro

This section presents our second contribution, a framework for proving 
correctness of cast representations. The framework is a theorem saying that for 
all cast representation $ C $, if $ C $ satisfies a collection of properties, 
then instantiating our parameterized space-efficient interpreter with $ C $ 
gives an interpter that is extensionally equal to the standard interpreter for 
\lazyD\ cast calculus. We are working on a similar theorem for \lazyUD{}.

@@

To use our framework, users needs to prove that their cast representation 
implements Lazy D Cast ADT (Definition~\ref{def:surely-lazyd}).
The definition confines the behavior of $ applyCast(v,c) $ so narrowly that it 
allows the framework to apply casts without referring to the actual definition 
of $ applyCast(v,c) $. This 
is because every casts at runtime is constructed by one of 
the three cast constructors. 
Property (1) handles casts constructed by $ id(T) $. 
And property (2) handles $ seq(c,c) $, which says applying the 
composition of $ c_1 $ and $ c_2 $ is the same as applying $ c_1 $ then $ c_2 $.
All remaining properties handles $ cast(T,l,T) $. They are effectively a 
duplication of the $ applyCast(v,c) $ in \ineffCEKD\ 
(Fig.~\ref{fig:applyCast-D-C}).

@@

@@

Some cast representations are also \textit{monoids}. They are useful in the 
proof of our framework, and might be interesting elsewhere.

@@

In subsection~\ref{ssec:framework:cek}, we introduce \effCEK{C}, a family 
of space-efficient semantics indexed by Cast ADTs ($ C $). 
In subsection~\ref{secc:framework:monoid-correct}, we prove when $ C $ is
a Lazy D Cast ADT and a monoid as well, $ \judgeDeval{e}{o} $ if 
and only if $ \judgeSeval{C}{e}{o} $. In 
subsection~\ref{secc:framework:all-correct}, we strengthen the theorem to drop 
the requirement that $ C $ must be a monoid, that is, every instance of Lazy D 
Cast ADT is correct.

>>>>

This section presents our second contribution, a framework for proving 
correctness of cast representations. The framework is a theorem saying that for 
all cast representation $ C $, if $ C $ satisfies a collection of properties, 
then it would respect the Lazy D semantics of cast calculi. We are working on a 
similar theorem for \lazyUD{}.

%then instantiating our parameterized space-efficient interpreter with $ C $ 
%gives an interpter that is extensionally equal to the standard interpreter for 
%\lazyD\ cast calculus.

@@

To use our framework, users needs to prove that their cast representation 
implements Lazy D Cast ADT (Definition~\ref{def:surely-lazyd}). To be a Lazy D 
Cast ADT, $ id(T) $ must acts like the identity function. And $ seq(c,c) $ 
must acts like a sequence of casts. What's more, $ cast(T_1,l,T_2) $ must act 
like the Lazy D $ applyCast $ (Fig.~\ref{fig:applyCast-D-C}).

@@

%Lazy D Cast ADT confines the behavior of operators so narrowly that it 
%effectively allows us to ``run'' programs without referring to an actual 
%representation of cast.

@@

Some cast representations are also \textit{monoids}. This definition is useful 
in the proof of our framework, and might be interesting for other people.

@@

In subsection~\ref{ssec:framework:cek}, we introduce \effCEK{C}, a family 
of space-efficient semantics indexed by Cast ADT ($ C $). When $ C $ is a Lazy 
D Cast ADT, \effCEK{C} repects \ineffCEKD.
In subsection~\ref{secc:framework:monoid-correct}, we prove when $ C $ is
a Lazy D Cast ADT and a monoid as well, $ \judgeDeval{e}{o} $ if 
and only if $ \judgeSeval{C}{e}{o} $. In 
subsection~\ref{secc:framework:all-correct}, we further prove that when $ C $ is
a Lazy D Cast ADT, $ \judgeDeval{e}{o} $ if and only if $ \judgeSeval{C}{e}{o} 
$.
